Comparing Optimization Algorithms in the Fitting of Linear Mixed Models: Evaluating Speed and Accuracy using \pkg{lme4} in R and \pkg{lmm} in Julia

### 2015-09-24 inst/doc/Paper.Rnw
Changes to the plot, minor edits

<<fig=TRUE>>=
res$cvg<-rep("yes",nrow(res))
res$cvg[which(res$excess>.02)] <- "no"
res$cvg<-as.factor(res$cvg)
k<-ggplot(res, aes(x=log(reltime), y=opt))
k + geom_point(aes(color=cvg))
@

@@

Bates D, Maechler M, Bolker B and Walker S (2014). _lme4: Linear mixed-effects models using Eigen
  and S4_. R package version 1.1-7, <URL: http://CRAN.R-project.org/package=lme4>.

>>>>

\setkeys{Gin}{width=.99\textwidth}
<<fig=TRUE>>=
res$cvg<-rep("yes",nrow(res))
res$cvg[which(res$excess>.02)] <- "no"
res$cvg<-as.factor(res$cvg)
k<-ggplot(res, aes(x=log(reltime), y=opt))
k + geom_point(aes(color=cvg))+scale_x_log10()
@

@@

Bates D, Maechler M, Bolker B and Walker S (2014). \_lme4: Linear mixed-effects models using Eigen
  and S4_. R package version 1.1-7, <URL: http://CRAN.R-project.org/package=lme4>.

### 2015-09-24 inst/doc/Paper.tex
Changes to the plot, minor edits

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:30 2015
\begin{table}[!htp]
\centering
\begin{tabular}{rllrrrrrr}
  \hline
 & opt & dsname & n & p & np & excess & time & reltime \\ 
  \hline
1 & LD\_CCSAQ & Alfalfa &  72 &  12 &   1 & 0.00 & 0.00 & 1.13 \\ 
  2 & LD\_CCSAQ & AvgDailyGain &  32 &   8 &   1 & 0.00 & 0.00 & 0.82 \\ 
  3 & LD\_CCSAQ & AvgDailyGain &  32 &   5 &   1 & 0.00 & 0.00 & 0.93 \\ 
  4 & LD\_CCSAQ & BIB &  24 &   8 &   1 & 0.00 & 0.00 & 0.79 \\ 
  5 & LD\_CCSAQ & Bond &  21 &   3 &   1 & 0.00 & 0.00 & 1.03 \\ 
  6 & LD\_CCSAQ & bs10 & 1104 &   4 &  20 & 0.00 & 1.10 & 4.44 \\ 
  7 & LD\_CCSAQ & bs10 & 1104 &   4 &   8 & 39.99 & 0.04 & 0.56 \\ 
  8 & LD\_CCSAQ & cake & 270 &  18 &   1 & 0.00 & 0.00 & 1.37 \\ 
  9 & LD\_CCSAQ & Cultivation &  24 &   6 &   1 & 0.00 & 0.00 & 0.99 \\ 
  10 & LD\_CCSAQ & Demand &  77 &   5 &   2 & 3.22 & 0.01 & 0.81 \\ 
  11 & LD\_CCSAQ & dialectNL & 225866 &   4 &   6 & 0.00 & 6.99 & 3.99 \\ 
  12 & LD\_CCSAQ & Dyestuff2 &  30 &   1 &   1 & 0.00 & 0.00 & 0.68 \\ 
  13 & LD\_CCSAQ & Dyestuff &  30 &   1 &   1 & 0.00 & 0.00 & 1.02 \\ 
  14 & LD\_CCSAQ & ergoStool &  36 &   4 &   1 & 0.00 & 0.00 & 1.10 \\ 
  15 & LD\_CCSAQ & Exam & 4059 &   5 &   1 & 0.00 & 0.01 & 1.19 \\ 
  16 & LD\_CCSAQ & Exam & 4059 &   6 &   1 & 0.00 & 0.01 & 1.32 \\ 
  17 & LD\_CCSAQ & Gasoline &  32 &   2 &   1 & 0.00 & 0.00 & 0.82 \\ 
  18 & LD\_CCSAQ & gb12 & 512 &   8 &  20 & 0.00 & 3.52 & 17.48 \\ 
  19 & LD\_CCSAQ & gb12 & 512 &   8 &   8 & 103.18 & 0.02 & 0.56 \\ 
  20 & LD\_CCSAQ & HR & 120 &   7 &   3 & 0.00 & 0.01 & 1.22 \\ 
  21 & LD\_CCSAQ & Hsb82 & 7185 &   5 &   1 & 192.73 & 0.01 & 0.49 \\ 
  22 & LD\_CCSAQ & IncBlk &  24 &   8 &   1 & 0.56 & 0.00 & 0.66 \\ 
  23 & LD\_CCSAQ & kb07 & 1790 &   8 &  72 & 8.21 & 17.47 & 4.12 \\ 
  24 & LD\_CCSAQ & Mississippi &  37 &   3 &   1 & 0.93 & 0.00 & 0.67 \\ 
  25 & LD\_CCSAQ & mm0 & 69588 &   4 &   6 & 0.00 & 4.83 & 4.40 \\ 
  26 & LD\_CCSAQ & Oxboys & 234 &   2 &   3 & 136.79 & 0.02 & 0.71 \\ 
  27 & LD\_CCSAQ & PBIB &  60 &  15 &   1 & 0.00 & 0.00 & 1.00 \\ 
  28 & LD\_CCSAQ & Penicillin & 144 &   1 &   2 & 0.00 & 0.01 & 4.94 \\ 
  29 & LD\_CCSAQ & Semiconductor &  48 &  16 &   1 & 0.00 & 0.00 & 1.05 \\ 
  30 & LD\_CCSAQ & SIMS & 3691 &   2 &   3 & 3.61 & 0.13 & 0.99 \\ 
  31 & LD\_CCSAQ & sleepstudy & 180 &   2 &   3 & 0.00 & 0.01 & 1.75 \\ 
  32 & LD\_CCSAQ & sleepstudy & 180 &   2 &   2 & 0.00 & 0.00 & 1.13 \\ 
  33 & LD\_CCSAQ & TeachingII &  96 &  12 &   1 & 0.00 & 0.00 & 0.93 \\ 
  34 & LD\_CCSAQ & Weights & 399 &   6 &   3 & 99.13 & 0.02 & 0.51 \\ 
  35 & LD\_CCSAQ & WWheat &  60 &   2 &   3 & 18.20 & 0.01 & 0.68 \\ 
   \hline
\end{tabular}
\end{table}\end {center}

@@

% Wed Sep  9 17:45:31 2015

@@

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:31 2015
\begin{tabular}{rllr}
  \hline
 & opt & dsname & excess \\ 
  \hline
347 & LN\_BOBYQA & Alfalfa & 0.00 \\ 
  348 & LN\_BOBYQA & Animal & 0.00 \\ 
  349 & LN\_BOBYQA & Assay & 0.00 \\ 
  350 & LN\_BOBYQA & AvgDailyGain & 0.00 \\ 
  351 & LN\_BOBYQA & AvgDailyGain & 0.00 \\ 
  352 & LN\_BOBYQA & BIB & 0.00 \\ 
  353 & LN\_BOBYQA & Bond & 0.00 \\ 
  354 & LN\_BOBYQA & bs10 & 0.00 \\ 
  355 & LN\_BOBYQA & bs10 & 0.00 \\ 
  356 & LN\_BOBYQA & cake & 0.00 \\ 
  357 & LN\_BOBYQA & Chem97 & 0.00 \\ 
  358 & LN\_BOBYQA & Chem97 & 0.00 \\ 
  359 & LN\_BOBYQA & Cultivation & 0.00 \\ 
  360 & LN\_BOBYQA & d3 & 0.00 \\ 
  361 & LN\_BOBYQA & Demand & 0.00 \\ 
  362 & LN\_BOBYQA & dialectNL & 0.00 \\ 
  363 & LN\_BOBYQA & Dyestuff2 & 0.00 \\ 
  364 & LN\_BOBYQA & Dyestuff & 0.00 \\ 
  365 & LN\_BOBYQA & egsingle & 0.00 \\ 
  366 & LN\_BOBYQA & ergoStool & 0.00 \\ 
  367 & LN\_BOBYQA & Exam & 0.00 \\ 
  368 & LN\_BOBYQA & Exam & 0.00 \\ 
  369 & LN\_BOBYQA & Gasoline & 0.00 \\ 
  370 & LN\_BOBYQA & gb12 & 0.00 \\ 
  371 & LN\_BOBYQA & gb12 & 0.00 \\ 
  372 & LN\_BOBYQA & Genetics & 0.00 \\ 
  373 & LN\_BOBYQA & HR & 0.00 \\ 
  374 & LN\_BOBYQA & Hsb82 & 0.00 \\ 
  375 & LN\_BOBYQA & IncBlk & 0.00 \\ 
  376 & LN\_BOBYQA & InstEval & 0.00 \\ 
  377 & LN\_BOBYQA & InstEval & 0.00 \\ 
  378 & LN\_BOBYQA & kb07 & 0.02 \\ 
  379 & LN\_BOBYQA & kb07 & 0.00 \\ 
  380 & LN\_BOBYQA & Mississippi & 0.00 \\ 
  381 & LN\_BOBYQA & mm0 & 0.00 \\ 
  382 & LN\_BOBYQA & Oxboys & 0.00 \\ 
  383 & LN\_BOBYQA & Pastes & 0.00 \\ 
  384 & LN\_BOBYQA & PBIB & 0.00 \\ 
  385 & LN\_BOBYQA & Penicillin & 0.00 \\ 
  386 & LN\_BOBYQA & Poems & 0.00 \\ 
  387 & LN\_BOBYQA & ScotsSec & 0.00 \\ 
  388 & LN\_BOBYQA & Semi2 & 0.00 \\ 
  389 & LN\_BOBYQA & Semiconductor & 0.00 \\ 
  390 & LN\_BOBYQA & SIMS & 0.00 \\ 
  391 & LN\_BOBYQA & sleepstudy & 0.00 \\ 
  392 & LN\_BOBYQA & sleepstudy & 0.00 \\ 
  393 & LN\_BOBYQA & TeachingII & 0.00 \\ 
  394 & LN\_BOBYQA & Weights & 0.00 \\ 
  395 & LN\_BOBYQA & WWheat & 0.00 \\ 
   \hline
\end{tabular}\end {center}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="Nelder_Mead" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:31 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
777 & Nelder\_Mead & bs10 & 1104 &  20 & 71.39 & 145.37 & 588.68 \\ 
  783 & Nelder\_Mead & d3 & 130418 &   9 & 317.59 & 454.52 & 4.25 \\ 
  785 & Nelder\_Mead & dialectNL & 225866 &   6 & 181.63 & 54.54 & 31.16 \\ 
  793 & Nelder\_Mead & gb12 & 512 &  20 & 78.71 & 38.21 & 189.60 \\ 
  801 & Nelder\_Mead & kb07 & 1790 &  72 & 398.73 & 2825.46 & 667.02 \\ 
  802 & Nelder\_Mead & kb07 & 1790 &  16 & 403.48 & 269.44 & 383.09 \\ 
  803 & Nelder\_Mead & Mississippi &  37 &   1 & 0.04 & 0.02 & 20.40 \\ 
  804 & Nelder\_Mead & mm0 & 69588 &   6 & 181.63 & 76.87 & 70.07 \\ 
   \hline
\end{tabular}\end{Schunk}

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="NLOPT_LN_NELDERMEAD" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:31 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
659 & NLOPT\_LN\_NELDERMEAD & Assay &  60 &   2 & 0.06 & 0.04 & 14.18 \\ 
  664 & NLOPT\_LN\_NELDERMEAD & bs10 & 1104 &  20 & 0.97 & 88.29 & 357.52 \\ 
  670 & NLOPT\_LN\_NELDERMEAD & d3 & 130418 &   9 & 100.19 & 627.93 & 5.87 \\ 
  680 & NLOPT\_LN\_NELDERMEAD & gb12 & 512 &  20 & 0.84 & 52.41 & 260.10 \\ 
  688 & NLOPT\_LN\_NELDERMEAD & kb07 & 1790 &  72 & 88.77 & 2839.07 & 670.23 \\ 
  689 & NLOPT\_LN\_NELDERMEAD & kb07 & 1790 &  16 & 3.50 & 198.84 & 282.72 \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="NLOPT_LN_SBPLX" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:31 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
745 & NLOPT\_LN\_SBPLX & gb12 & 512 &  20 & 0.82 & 3.81 & 18.92 \\ 
  753 & NLOPT\_LN\_SBPLX & kb07 & 1790 &  72 & 4.97 & 564.69 & 133.31 \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="LN_BOBYQA" & dsname == "kb07")[c(1,2,5,6,7,9)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:31 2015
\begin{tabular}{rllrrrr}
  \hline
 & opt & dsname & np & excess & time & objective \\ 
  \hline
378 & LN\_BOBYQA & kb07 &  72 & 0.02 & 4.24 & 28586.33 \\ 
  379 & LN\_BOBYQA & kb07 &  16 & 0.00 & 0.70 & 28670.91 \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> res$cvg<-rep("yes",nrow(res))
> res$cvg[which(res$excess>.02)] <- "no"
> res$cvg<-as.factor(res$cvg)
> k<-ggplot(res, aes(x=log(reltime), y=opt))
> k + geom_point(aes(color=cvg))
\end{Sinput}
\end{Schunk}
\includegraphics{Paper-013}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="LN_BOBYQA" & time >= 0.2)[c("dsname","time","n","np","models")]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Wed Sep  9 17:45:31 2015
\begin{tabular}{rlrrrl}
  \hline
 & dsname & time & n & np & models \\ 
  \hline
354 & bs10 & 0.25 & 1104 &  20 & Y \~{} 1 + U + V + W + ((1 + U + V + W) $|$ G) + ((1 + U + V + W) $|$ H) \\ 
  360 & d3 & 106.94 & 130418 &   9 & Y \~{} 1 + U + ((1 + U) $|$ G) + ((1 + U) $|$ H) + ((1 + U) $|$ I) \\ 
  362 & dialectNL & 1.75 & 225866 &   6 & Y \~{} 1 + A + U + V + W + X + Z + T + (1 $|$ G) + ((0 + V + W + X) $|$ G) + ((1 + A + Z) $|$ H) + (1 $|$ I) \\ 
  370 & gb12 & 0.20 & 512 &  20 & Y \~{} 1 + S + T + U + V + W + X + Z + ((1 + S + U + W) $|$ G) + ((1 + S + T + V) $|$ H) \\ 
  376 & InstEval & 2.35 & 73421 &   2 & Y \~{} 1 + I * A + (1 $|$ G) + (1 $|$ H) \\ 
  377 & InstEval & 4.36 & 73421 &   3 & Y \~{} 1 + A + (1 $|$ G) + (1 $|$ H) + (1 $|$ I) \\ 
  378 & kb07 & 4.24 & 1790 &  72 & Y \~{} 1 + S + T + U + V + W + X + Z + ((1 + S + T + U + V + W + X + Z) $|$ G) + ((1 + S + T + U + V + W + X + Z) $|$ H) \\ 
  379 & kb07 & 0.70 & 1790 &  16 & Y \~{} 1 + S + T + U + V + W + X + Z + (1 $|$ G) + ((0 + S) $|$ G) + ((0 + T) $|$ G) + ((0 + U) $|$ G) + ((0 + V) $|$ G) + ((0 + W) $|$ G) + ((0 + X) $|$ G) + ((0 + Z) $|$ G) + (1 $|$ H) + ((0 + S) $|$ H) + ((0 + T) $|$ H) + ((0 + U) $|$ H) + ((0 + V) $|$ H) + ((0 + W) $|$ H) + ((0 + X) $|$ H) + ((0 + Z) $|$ H) \\ 
  381 & mm0 & 1.10 & 69588 &   6 & Y \~{} 1 + A * U + ((1 + U) $|$ G) + ((1 + U) $|$ H) \\ 
  386 & Poems & 5.69 & 275996 &   3 & Y \~{} 1 + U + V + (1 $|$ G) + (1 $|$ H) + (1 $|$ I) \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\begin{Schunk}
\begin{Soutput}
@Manual{,
  title = {{lme4}: Linear mixed-effects models using Eigen and S4},
  author = {Douglas Bates and Martin Maechler and Ben Bolker and Steven Walker},
  year = {2014},
  note = {R package version 1.1-7},
  url = {http://CRAN.R-project.org/package=lme4},
}

>>>>

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:30 2015
\begin{table}[!htp]
\centering
\begin{tabular}{rllrrrrrr}
  \hline
 & opt & dsname & n & p & np & excess & time & reltime \\ 
  \hline
1 & LD\_CCSAQ & Alfalfa &  72 &  12 &   1 & 0.00 & 0.00 & 1.13 \\ 
  2 & LD\_CCSAQ & AvgDailyGain &  32 &   8 &   1 & 0.00 & 0.00 & 0.82 \\ 
  3 & LD\_CCSAQ & AvgDailyGain &  32 &   5 &   1 & 0.00 & 0.00 & 0.93 \\ 
  4 & LD\_CCSAQ & BIB &  24 &   8 &   1 & 0.00 & 0.00 & 0.79 \\ 
  5 & LD\_CCSAQ & Bond &  21 &   3 &   1 & 0.00 & 0.00 & 1.03 \\ 
  6 & LD\_CCSAQ & bs10 & 1104 &   4 &  20 & 0.00 & 1.10 & 4.44 \\ 
  7 & LD\_CCSAQ & bs10 & 1104 &   4 &   8 & 39.99 & 0.04 & 0.56 \\ 
  8 & LD\_CCSAQ & cake & 270 &  18 &   1 & 0.00 & 0.00 & 1.37 \\ 
  9 & LD\_CCSAQ & Cultivation &  24 &   6 &   1 & 0.00 & 0.00 & 0.99 \\ 
  10 & LD\_CCSAQ & Demand &  77 &   5 &   2 & 3.22 & 0.01 & 0.81 \\ 
  11 & LD\_CCSAQ & dialectNL & 225866 &   4 &   6 & 0.00 & 6.99 & 3.99 \\ 
  12 & LD\_CCSAQ & Dyestuff2 &  30 &   1 &   1 & 0.00 & 0.00 & 0.68 \\ 
  13 & LD\_CCSAQ & Dyestuff &  30 &   1 &   1 & 0.00 & 0.00 & 1.02 \\ 
  14 & LD\_CCSAQ & ergoStool &  36 &   4 &   1 & 0.00 & 0.00 & 1.10 \\ 
  15 & LD\_CCSAQ & Exam & 4059 &   5 &   1 & 0.00 & 0.01 & 1.19 \\ 
  16 & LD\_CCSAQ & Exam & 4059 &   6 &   1 & 0.00 & 0.01 & 1.32 \\ 
  17 & LD\_CCSAQ & Gasoline &  32 &   2 &   1 & 0.00 & 0.00 & 0.82 \\ 
  18 & LD\_CCSAQ & gb12 & 512 &   8 &  20 & 0.00 & 3.52 & 17.48 \\ 
  19 & LD\_CCSAQ & gb12 & 512 &   8 &   8 & 103.18 & 0.02 & 0.56 \\ 
  20 & LD\_CCSAQ & HR & 120 &   7 &   3 & 0.00 & 0.01 & 1.22 \\ 
  21 & LD\_CCSAQ & Hsb82 & 7185 &   5 &   1 & 192.73 & 0.01 & 0.49 \\ 
  22 & LD\_CCSAQ & IncBlk &  24 &   8 &   1 & 0.56 & 0.00 & 0.66 \\ 
  23 & LD\_CCSAQ & kb07 & 1790 &   8 &  72 & 8.21 & 17.47 & 4.12 \\ 
  24 & LD\_CCSAQ & Mississippi &  37 &   3 &   1 & 0.93 & 0.00 & 0.67 \\ 
  25 & LD\_CCSAQ & mm0 & 69588 &   4 &   6 & 0.00 & 4.83 & 4.40 \\ 
  26 & LD\_CCSAQ & Oxboys & 234 &   2 &   3 & 136.79 & 0.02 & 0.71 \\ 
  27 & LD\_CCSAQ & PBIB &  60 &  15 &   1 & 0.00 & 0.00 & 1.00 \\ 
  28 & LD\_CCSAQ & Penicillin & 144 &   1 &   2 & 0.00 & 0.01 & 4.94 \\ 
  29 & LD\_CCSAQ & Semiconductor &  48 &  16 &   1 & 0.00 & 0.00 & 1.05 \\ 
  30 & LD\_CCSAQ & SIMS & 3691 &   2 &   3 & 3.61 & 0.13 & 0.99 \\ 
  31 & LD\_CCSAQ & sleepstudy & 180 &   2 &   3 & 0.00 & 0.01 & 1.75 \\ 
  32 & LD\_CCSAQ & sleepstudy & 180 &   2 &   2 & 0.00 & 0.00 & 1.13 \\ 
  33 & LD\_CCSAQ & TeachingII &  96 &  12 &   1 & 0.00 & 0.00 & 0.93 \\ 
  34 & LD\_CCSAQ & Weights & 399 &   6 &   3 & 99.13 & 0.02 & 0.51 \\ 
  35 & LD\_CCSAQ & WWheat &  60 &   2 &   3 & 18.20 & 0.01 & 0.68 \\ 
   \hline
\end{tabular}
\end{table}\end {center}

@@

% Thu Sep 24 15:26:30 2015

@@

\begin
{center}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:30 2015
\begin{tabular}{rllr}
  \hline
 & opt & dsname & excess \\ 
  \hline
347 & LN\_BOBYQA & Alfalfa & 0.00 \\ 
  348 & LN\_BOBYQA & Animal & 0.00 \\ 
  349 & LN\_BOBYQA & Assay & 0.00 \\ 
  350 & LN\_BOBYQA & AvgDailyGain & 0.00 \\ 
  351 & LN\_BOBYQA & AvgDailyGain & 0.00 \\ 
  352 & LN\_BOBYQA & BIB & 0.00 \\ 
  353 & LN\_BOBYQA & Bond & 0.00 \\ 
  354 & LN\_BOBYQA & bs10 & 0.00 \\ 
  355 & LN\_BOBYQA & bs10 & 0.00 \\ 
  356 & LN\_BOBYQA & cake & 0.00 \\ 
  357 & LN\_BOBYQA & Chem97 & 0.00 \\ 
  358 & LN\_BOBYQA & Chem97 & 0.00 \\ 
  359 & LN\_BOBYQA & Cultivation & 0.00 \\ 
  360 & LN\_BOBYQA & d3 & 0.00 \\ 
  361 & LN\_BOBYQA & Demand & 0.00 \\ 
  362 & LN\_BOBYQA & dialectNL & 0.00 \\ 
  363 & LN\_BOBYQA & Dyestuff2 & 0.00 \\ 
  364 & LN\_BOBYQA & Dyestuff & 0.00 \\ 
  365 & LN\_BOBYQA & egsingle & 0.00 \\ 
  366 & LN\_BOBYQA & ergoStool & 0.00 \\ 
  367 & LN\_BOBYQA & Exam & 0.00 \\ 
  368 & LN\_BOBYQA & Exam & 0.00 \\ 
  369 & LN\_BOBYQA & Gasoline & 0.00 \\ 
  370 & LN\_BOBYQA & gb12 & 0.00 \\ 
  371 & LN\_BOBYQA & gb12 & 0.00 \\ 
  372 & LN\_BOBYQA & Genetics & 0.00 \\ 
  373 & LN\_BOBYQA & HR & 0.00 \\ 
  374 & LN\_BOBYQA & Hsb82 & 0.00 \\ 
  375 & LN\_BOBYQA & IncBlk & 0.00 \\ 
  376 & LN\_BOBYQA & InstEval & 0.00 \\ 
  377 & LN\_BOBYQA & InstEval & 0.00 \\ 
  378 & LN\_BOBYQA & kb07 & 0.02 \\ 
  379 & LN\_BOBYQA & kb07 & 0.00 \\ 
  380 & LN\_BOBYQA & Mississippi & 0.00 \\ 
  381 & LN\_BOBYQA & mm0 & 0.00 \\ 
  382 & LN\_BOBYQA & Oxboys & 0.00 \\ 
  383 & LN\_BOBYQA & Pastes & 0.00 \\ 
  384 & LN\_BOBYQA & PBIB & 0.00 \\ 
  385 & LN\_BOBYQA & Penicillin & 0.00 \\ 
  386 & LN\_BOBYQA & Poems & 0.00 \\ 
  387 & LN\_BOBYQA & ScotsSec & 0.00 \\ 
  388 & LN\_BOBYQA & Semi2 & 0.00 \\ 
  389 & LN\_BOBYQA & Semiconductor & 0.00 \\ 
  390 & LN\_BOBYQA & SIMS & 0.00 \\ 
  391 & LN\_BOBYQA & sleepstudy & 0.00 \\ 
  392 & LN\_BOBYQA & sleepstudy & 0.00 \\ 
  393 & LN\_BOBYQA & TeachingII & 0.00 \\ 
  394 & LN\_BOBYQA & Weights & 0.00 \\ 
  395 & LN\_BOBYQA & WWheat & 0.00 \\ 
   \hline
\end{tabular}\end {center}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="Nelder_Mead" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:30 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
777 & Nelder\_Mead & bs10 & 1104 &  20 & 71.39 & 145.37 & 588.68 \\ 
  783 & Nelder\_Mead & d3 & 130418 &   9 & 317.59 & 454.52 & 4.25 \\ 
  785 & Nelder\_Mead & dialectNL & 225866 &   6 & 181.63 & 54.54 & 31.16 \\ 
  793 & Nelder\_Mead & gb12 & 512 &  20 & 78.71 & 38.21 & 189.60 \\ 
  801 & Nelder\_Mead & kb07 & 1790 &  72 & 398.73 & 2825.46 & 667.02 \\ 
  802 & Nelder\_Mead & kb07 & 1790 &  16 & 403.48 & 269.44 & 383.09 \\ 
  803 & Nelder\_Mead & Mississippi &  37 &   1 & 0.04 & 0.02 & 20.40 \\ 
  804 & Nelder\_Mead & mm0 & 69588 &   6 & 181.63 & 76.87 & 70.07 \\ 
   \hline
\end{tabular}\end{Schunk}

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="NLOPT_LN_NELDERMEAD" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:30 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
659 & NLOPT\_LN\_NELDERMEAD & Assay &  60 &   2 & 0.06 & 0.04 & 14.18 \\ 
  664 & NLOPT\_LN\_NELDERMEAD & bs10 & 1104 &  20 & 0.97 & 88.29 & 357.52 \\ 
  670 & NLOPT\_LN\_NELDERMEAD & d3 & 130418 &   9 & 100.19 & 627.93 & 5.87 \\ 
  680 & NLOPT\_LN\_NELDERMEAD & gb12 & 512 &  20 & 0.84 & 52.41 & 260.10 \\ 
  688 & NLOPT\_LN\_NELDERMEAD & kb07 & 1790 &  72 & 88.77 & 2839.07 & 670.23 \\ 
  689 & NLOPT\_LN\_NELDERMEAD & kb07 & 1790 &  16 & 3.50 & 198.84 & 282.72 \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="NLOPT_LN_SBPLX" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:30 2015
\begin{tabular}{rllrrrrr}
  \hline
 & opt & dsname & n & np & excess & time & reltime \\ 
  \hline
745 & NLOPT\_LN\_SBPLX & gb12 & 512 &  20 & 0.82 & 3.81 & 18.92 \\ 
  753 & NLOPT\_LN\_SBPLX & kb07 & 1790 &  72 & 4.97 & 564.69 & 133.31 \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="LN_BOBYQA" & dsname == "kb07")[c(1,2,5,6,7,9)]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:30 2015
\begin{tabular}{rllrrrr}
  \hline
 & opt & dsname & np & excess & time & objective \\ 
  \hline
378 & LN\_BOBYQA & kb07 &  72 & 0.02 & 4.24 & 28586.33 \\ 
  379 & LN\_BOBYQA & kb07 &  16 & 0.00 & 0.70 & 28670.91 \\ 
   \hline
\end{tabular}\end{Schunk}

@@

\setkeys{Gin}{width=.99\textwidth}
\begin{Schunk}
\begin{Sinput}
> res$cvg<-rep("yes",nrow(res))
> res$cvg[which(res$excess>.02)] <- "no"
> res$cvg<-as.factor(res$cvg)
> k<-ggplot(res, aes(x=log(reltime), y=opt))
> k + geom_point(aes(color=cvg))+scale_x_log10()
\end{Sinput}
\end{Schunk}
\includegraphics{Paper-013}

@@

\begin{Schunk}
\begin{Sinput}
> print(xtable(subset(res, opt=="LN_BOBYQA" & time >= 0.2)[c("dsname","time","n","np","models")]),floating=FALSE, table.placement="H")
\end{Sinput}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Thu Sep 24 15:26:31 2015
\begin{tabular}{rlrrrl}
  \hline
 & dsname & time & n & np & models \\ 
  \hline
354 & bs10 & 0.25 & 1104 &  20 & Y \~{} 1 + U + V + W + ((1 + U + V + W) $|$ G) + ((1 + U + V + W) $|$ H) \\ 
  360 & d3 & 106.94 & 130418 &   9 & Y \~{} 1 + U + ((1 + U) $|$ G) + ((1 + U) $|$ H) + ((1 + U) $|$ I) \\ 
  362 & dialectNL & 1.75 & 225866 &   6 & Y \~{} 1 + A + U + V + W + X + Z + T + (1 $|$ G) + ((0 + V + W + X) $|$ G) + ((1 + A + Z) $|$ H) + (1 $|$ I) \\ 
  370 & gb12 & 0.20 & 512 &  20 & Y \~{} 1 + S + T + U + V + W + X + Z + ((1 + S + U + W) $|$ G) + ((1 + S + T + V) $|$ H) \\ 
  376 & InstEval & 2.35 & 73421 &   2 & Y \~{} 1 + I * A + (1 $|$ G) + (1 $|$ H) \\ 
  377 & InstEval & 4.36 & 73421 &   3 & Y \~{} 1 + A + (1 $|$ G) + (1 $|$ H) + (1 $|$ I) \\ 
  378 & kb07 & 4.24 & 1790 &  72 & Y \~{} 1 + S + T + U + V + W + X + Z + ((1 + S + T + U + V + W + X + Z) $|$ G) + ((1 + S + T + U + V + W + X + Z) $|$ H) \\ 
  379 & kb07 & 0.70 & 1790 &  16 & Y \~{} 1 + S + T + U + V + W + X + Z + (1 $|$ G) + ((0 + S) $|$ G) + ((0 + T) $|$ G) + ((0 + U) $|$ G) + ((0 + V) $|$ G) + ((0 + W) $|$ G) + ((0 + X) $|$ G) + ((0 + Z) $|$ G) + (1 $|$ H) + ((0 + S) $|$ H) + ((0 + T) $|$ H) + ((0 + U) $|$ H) + ((0 + V) $|$ H) + ((0 + W) $|$ H) + ((0 + X) $|$ H) + ((0 + Z) $|$ H) \\ 
  381 & mm0 & 1.10 & 69588 &   6 & Y \~{} 1 + A * U + ((1 + U) $|$ G) + ((1 + U) $|$ H) \\ 
  386 & Poems & 5.69 & 275996 &   3 & Y \~{} 1 + U + V + (1 $|$ G) + (1 $|$ H) + (1 $|$ I) \\ 
   \hline
\end{tabular}\end{Schunk}

@@

Douglas Bates, Katharine M. Mullen, John C. Nash and Ravi Varadhan (2014). minqa:
  Derivative-free optimization algorithms by quadratic approximation. R package version 1.2.4.
  http://CRAN.R-project.org/package=minqa

Bates D, Maechler M, Bolker B and Walker S (2014). _lme4: Linear mixed-effects models using Eigen
  and S4_. R package version 1.1-7, <URL: http://CRAN.R-project.org/package=lme4>.

John C. Nash, Ravi Varadhan (2011). Unifying Optimization Algorithms to Aid Software System
  Users: optimx for R. Journal of Statistical Software, 43(9), 1-14. URL
  http://www.jstatsoft.org/v43/i09/.

Jeroen Ooms (2014). The jsonlite Package: A Practical and Consistent Mapping Between JSON Data
  and R Objects. arXiv:1403.2805 [stat.CO] URL http://arxiv.org/abs/1403.2805.

Steven G. Johnson, The NLopt nonlinear-optimization package, http://ab-initio.mit.edu/nlopt

(For the nloptr package they want us to go through and cite each algorithm we used)
